A possibilistic valid-time model

### 2011-11-10 ipmu2012/preliminaries.tex
update

@@

\paragraph{Example} Consider the ill-known values $X = \left[5, 2, 8\right]$ and $Y = \left[9, 7, 10 \right]$. The knowledge about the evaluation of the interval $\left[a, b \right]$  is given by the expressions \eqref{eq:interval-pos},\eqref{eq:interval-nec}.  Figure~\ref{fig:3d-possibility} shows a 3D plot of the possibility that an interval $[a,b]$ passes the evaluations specified by the ill-known constraints. Note the triangular form for the resulting possibility distribution since the condition $a \leq b$ holds.

\begin{figure}[h!]
\centering
\includegraphics[scale=0.4]{graphs/3D_possibility.eps}
\caption{Possibility of evaluation for the interval $[a,b]$.}
\label{fig:3d-possibility}
\end{figure}
The necessity plot is obtained in a similar way and is shown in Figure~\ref{fig:3d-necessity}. Notice that the necessity measure is not normalized because the supports of $X$ and $Y$ overlap.
\begin{figure}[h!]
\centering
\includegraphics[scale=0.4]{graphs/3D_necessity.eps}
\caption{Necessity of evaluation for the interval $[a,b]$.}
\label{fig:3d-necessity}
\end{figure}

\subsection{Temporal databases}
%In this section, the proposed reasoning is applied to the specific context of intervals on the real line. This setting is of specific interest in the context of fuzzy temporal databases.
A temporal database \cite{Dyreson1994} is a database that manages some aspects of time in its schema. A \textbf{chronon} is the shortest duration of time supported by the database. The time can be represented either as points or intervals \cite{655777}. Fuzzy temporal models \cite{4481150} are proposed when the time points or intervals are not precisely known. There are proposals for the  fuzzyfication of the time point \cite{Dubois89} and the fuzzyfication of the time interval \cite{Garrido2009}.\\
Allen \cite{Allen:1983:MKT:182.358434} studied the comparison between two crisp time intervals. For fuzzy intervals, several proposals \cite{4481150}, \cite{springerlink:10.1007/978-3-540-39964-3_57},\cite{10.1109/TIME.2004.1314418} have been done.

@@

Fuzzy temporal models \cite{4481150} deal with time points \cite{Dubois89} or intervals \cite{Garrido2009} that are ill-known. Some fuzzy temporal models assume that the time stored in the database is an interval. The temporal interval is represented by two ill-known time points: $X$  an ill-known starting point and $Y$ an ill-known ending point. The interval $\left[X,Y\right]$ is not a fuzzy interval but an ill-known interval: it is a crisp interval but it is partially unknown which values are in this interval.

>>>>

%Introductory text:
This background section is dedicated to introduce some basic concepts about possibilistic variables, the differences between fuzzy numbers and intervals. The interval evaluation by means of ill-known constraints is explained.

The preliminaries section concludes with a brief introduction to temporal databases.

@@

%\paragraph{Example} Consider the ill-known values $X = \left[5, 2, 8\right]$ and $Y = \left[9, 7, 10 \right]$. The knowledge about the evaluation of the interval $\left[a, b \right]$  is given by the expressions \eqref{eq:interval-pos},\eqref{eq:interval-nec}.  Figure~\ref{fig:3d-possibility} shows a 3D plot of the possibility that an interval $[a,b]$ passes the evaluations specified by the ill-known constraints. Note the triangular form for the resulting possibility distribution since the condition $a \leq b$ holds.
%
%\begin{figure}[h!]
%\centering
%\includegraphics[scale=0.4]{graphs/3D_possibility.eps}
%\caption{Possibility of evaluation for the interval $[a,b]$.}
%\label{fig:3d-possibility}
%\end{figure}
%The necessity plot is obtained in a similar way and is shown in Figure~\ref{fig:3d-necessity}. Notice that the necessity measure is not normalized because the supports of $X$ and $Y$ overlap.
%\begin{figure}[h!]
%\centering
%\includegraphics[scale=0.4]{graphs/3D_necessity.eps}
%\caption{Necessity of evaluation for the interval $[a,b]$.}
%\label{fig:3d-necessity}
%\end{figure}

\subsection{Temporal databases}
%In this section, the proposed reasoning is applied to the specific context of intervals on the real line. This setting is of specific interest in the context of fuzzy temporal databases.
A temporal database \cite{Dyreson1994} is a database that manages some aspects of time in its schema. A \textbf{chronon} is the shortest duration of time supported by the database. The time can be represented either as points or intervals \cite{655777}. Fuzzy temporal models \cite{schockaert08} are proposed when the time points or intervals are not precisely known. There are proposals for the  fuzzyfication of the time point \cite{Dubois89} and the fuzzyfication of the time interval \cite{Garrido2009}.\\
Allen \cite{Allen83} studied the comparison between two crisp time intervals. For fuzzy intervals, several proposals \cite{ohlbach04,nagypal03,schockaert08} have been done.

@@

Fuzzy temporal models \cite{schockaert08} deal with time points \cite{Dubois89} or intervals \cite{Garrido2009} that are ill-known. Some fuzzy temporal models assume that the time stored in the database is an interval. The temporal interval is represented by two ill-known time points: $X$  an ill-known starting point and $Y$ an ill-known ending point. The interval $\left[X,Y\right]$ is not a fuzzy interval but an ill-known interval: it is a crisp interval but it is partially unknown which values are in this interval.

### 2011-11-10 ipmu2012/proposal.tex
update

\subsection{Representation of ill-known valid-time intervals}

>>>>

The proposal consist on a possibilistic valid-time model. The representation and the querying are explained in the following subsections.

\subsection{Representation of ill-known valid-time intervals}
Valid time is usually represented as an interval. The interval has a starting and an ending points. An ill-known valid-time interval is an interval in witch one or both points are ill-known.

\begin{definition}
A possibilistic valid-time period \emph{PVT} is a possibilistic interval defined by means of two ill-known points, namely $\left[ X,\ Y \right]$
\begin{equation}
PVT = \left[X,\ Y \right] 
\end{equation}
X and Y are ill-known values in the set of the real numbers $\mathbb{R}$. The uncertainty about the values taken by $X$ and $Y$ are given by the possibility distributions $\pi_X$ and $\pi_Y$.
\end{definition}
